\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-13 paper/sp.tex
refs

\begin{thebibliography}{}
\bibitem[Abolfathi \etal(2018)]{dr14} Abolfathi, B., Aguado, D.~S., Aguilar, G., \etal\ 2018, \apjs, 235, 42 
\bibitem[Astropy Collaboration \etal(2013)]{astropy} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., \etal\ 2013, \aap, 558, A33 
\bibitem[Astropy Collaboration \etal(2018)]{astropy2} The Astropy Collaboration, Price-Whelan, A.~M., Sip{\H o}cz, B.~M., \etal\ 2018, arXiv:1801.02634 
\bibitem[Bailer-Jones et al.(2018)]{calj} Bailer-Jones, C.~A.~L., Rybizki, J., Fouesneau, M., Mantelet, G., \& Andrae, R.\ 2018, \aj, 156, 58 
\bibitem[Blanton \etal(2017)]{sdssiv} Blanton, M.~R., Bershady, M.~A., Abolfathi, B., \etal\ 2017, \aj, 154, 28 
\bibitem[Hogg(2018)]{gaialf} Hogg, D.~W.\ 2018, arXiv:1804.07766
\bibitem[Hunter(2007)]{matplotlib} Hunter, J.~D.\ 2007, CISE, 9(3), 90
\bibitem[Jones \etal(2001)]{scipy} Jones, E., Oliphant, E., Peterson, P. \etal\ 2001, \url{http://www.scipy.org/}
\bibitem[Kollmeier \etal(2017)]{sdssv} Kollmeier, J.~A., Zasowski, G., Rix, H.-W., \etal\ 2017, arXiv:1711.03234 
\bibitem[Lindegren \etal(2018)]{lindegren} Lindegren, L., Hernandez, J., Bombrun, A., \etal\ 2018, arXiv:1804.09366 
\bibitem[Lutz \& Kelker(1973)]{lk} Lutz, T.~E., \& Kelker, D.~H.\ 1973, \pasp, 85, 573 
\bibitem[Martig \etal(2016)]{martig} Martig, M., Fouesneau, M., Rix, H.-W., \etal\ 2016, \mnras, 456, 3655 
\bibitem[Ness \etal(2015)]{cannon} Ness, M., Hogg, D.~W., Rix, H.-W., Ho, A.~Y.~Q., \& Zasowski, G.\ 2015, \apj, 808, 16 
\bibitem[Ness \etal(2016)]{nessage} Ness, M., Hogg, D.~W., Rix, H.-W., \etal\ 2016, \apj, 823, 114 
\bibitem[Oliphant(2006)]{numpy} Oliphant, T.~E.\ 2006, \emph{A guide to NumPy}, Trelgol Publishing
\bibitem[P\'erez \& Granger(2007)]{ipython} P\'erez, F. \& Granger, B.~E.\ 2007, CISE, 9(3), 29
\bibitem[Skrutskie \etal(2006)]{zmass} Skrutskie, M.~F., Cutri, R.~M., Stiening, R., \etal\ 2006, \aj, 131, 1163 
\end{thebibliography}

>>>>

\begin{thebibliography}{}
\bibitem[Abolfathi \etal(2018)]{dr14} Abolfathi, B., Aguado, D.~S., Aguilar, G., \etal\ 2018, \apjs, 235, 42 
\bibitem[Astropy Collaboration \etal(2013)]{astropy} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., \etal\ 2013, \aap, 558, A33 
\bibitem[Astropy Collaboration \etal(2018)]{astropy2} The Astropy Collaboration, Price-Whelan, A.~M., Sip{\H o}cz, B.~M., \etal\ 2018, arXiv:1801.02634 
\bibitem[Bailer-Jones \etal(2018)]{calj} Bailer-Jones, C.~A.~L., Rybizki, J., Fouesneau, M., Mantelet, G., \& Andrae, R.\ 2018, \aj, 156, 58 
\bibitem[Blanton \etal(2017)]{sdssiv} Blanton, M.~R., Bershady, M.~A., Abolfathi, B., \etal\ 2017, \aj, 154, 28 
\bibitem[Casey \etal(2016)]{casey} Casey, A.~R., Hogg, D.~W., Ness, M., \etal\ 2016, arXiv:1603.03040 
\bibitem[Ho \etal(2017)]{ho} Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W., \etal\ 2017, \apj, 836, 5 
\bibitem[Hogg(2018)]{gaialf} Hogg, D.~W.\ 2018, arXiv:1804.07766
\bibitem[Hunter(2007)]{matplotlib} Hunter, J.~D.\ 2007, CISE, 9(3), 90
\bibitem[Jones \etal(2001)]{scipy} Jones, E., Oliphant, E., Peterson, P. \etal\ 2001, \url{http://www.scipy.org/}
\bibitem[Kollmeier \etal(2017)]{sdssv} Kollmeier, J.~A., Zasowski, G., Rix, H.-W., \etal\ 2017, arXiv:1711.03234 
\bibitem[Lindegren \etal(2018)]{lindegren} Lindegren, L., Hernandez, J., Bombrun, A., \etal\ 2018, arXiv:1804.09366 
\bibitem[Lutz \& Kelker(1973)]{lk} Lutz, T.~E., \& Kelker, D.~H.\ 1973, \pasp, 85, 573 
\bibitem[Martig \etal(2016)]{martig} Martig, M., Fouesneau, M., Rix, H.-W., \etal\ 2016, \mnras, 456, 3655 
\bibitem[Ness \etal(2015)]{cannon} Ness, M., Hogg, D.~W., Rix, H.-W., Ho, A.~Y.~Q., \& Zasowski, G.\ 2015, \apj, 808, 16 
\bibitem[Ness \etal(2016)]{nessage} Ness, M., Hogg, D.~W., Rix, H.-W., \etal\ 2016, \apj, 823, 114 
\bibitem[Ness \etal(2018)]{nessdopp} Ness, M., Rix, H.-W., Hogg, D.~W., \etal\ 2018, \apj, 853, 198 
\bibitem[Oliphant(2006)]{numpy} Oliphant, T.~E.\ 2006, \emph{A guide to NumPy}, Trelgol Publishing
\bibitem[P\'erez \& Granger(2007)]{ipython} P\'erez, F. \& Granger, B.~E.\ 2007, CISE, 9(3), 29
\bibitem[Skrutskie \etal(2006)]{zmass} Skrutskie, M.~F., Cutri, R.~M., Stiening, R., \etal\ 2006, \aj, 131, 1163 
\end{thebibliography}
